Explaining NonLinear Classification Decisions with Deep Taylor Decomposition\\ analysis

### 2022-06-03 Präsentation/Präsentation_23.06.2020.tex
presentation

>>>>

\subsection[Example MINST]{Example MNIST}

\begin{frame}
\frametitle{Example MNIST: Setting}
Training of a neural network to detect a handwritten digit between 0-3 next to a distractor digit from 4-9 given teh following setting:
\begin{itemize}
\item images of size 28 x 56 pixels
\item $28 x 56 = 1568$ input neurons $\{x_i\}$, one hidden layer with 400 neurons $\{x_j\}$ and one output $x_k$
\item weights are random initializated $\{w_{ij}\}$ and bias $\{b_j\}$ is initialized to zero and non negative during training
\item Training with 300000 iterations of stochastic gradient descent with a bach size of 20
\item 
\end{itemize}

\begin{frame}
\frametitle{Example MNIST: Heatmaps}
\vspace{0.5cm}
\begin{figure}
\includegraphics[height=2.5cm, width=12cm]{image/example_mnist_heatmap}
\end{figure}

\begin{figure}
\includegraphics[height=3.25cm, width=12cm]{image/example_mnist_consistent}
\vspace{-0.75cm}
\caption{Heatmap and Empirical Results of Consistency}
\end{figure}

\section[Application to Deep Networks]{Application to Deep Networks}

\begin{frame}
\frametitle{Min-Max Relevance Model}
Trainable relevnce model designed to incorporate bottom-up and top-down information

\begin{align*}
y_i &= \max(0,\sum_ix_iv_{ij} + a_j)\\
\hat{R}_k &= \sum_j y_j,
\end{align*}
where $a_j = \min(0,\sum_l R_l V_{lj} + d_j)$ is a negative bias.\\
$\rightarrow$ Compute $\{v_{ij}, v_{lj},d_j\}$ by minimizing 
\begin{equation*}
\min\langle (\hat{R}_k-R_k)^2) \rangle
\end{equation*}
\vspace{-1cm}
\end{frame}

\subsection[Relevance Model]{Relevance Model}

\begin{frame}
\frametitle{Deep Networks}
Many problems require very complex deep architectures

\begin{figure}
\includegraphics[height=6cm, width=11cm]{image/example_deep_network_one}
\vspace{-0.25cm}
\caption{Example Deep Network}
\end{figure}

\vspace{-1cm}
\end{frame}
